### 2022-12-20 submission/manuscript.Rmd
Render with table, edits, and track changes

The *Riffomonas* YouTube channel (https://www.youtube.com/c/RiffomonasProject) seeks to fill this gap. I started consistently posting videos at the beginning of the COVID-19 pandemic in the Spring of 2020. As of the end of November 2022, the channel included 285 videos that had been viewed 635,947 times; the channel had 11,327 subscribers. The majority of these are 264 videos in the "Code Club" playlist [@Hagan2020]. Other videos are related to a previously described tutorial series on reproducible research [@Schloss2018a] and series where reproducible reseach practices are used to address topical questions. Code Club videos are typically between 20 and 30 minutes long. The code that is developed in the videos is available through a website (https://riffomonas.org/code_club/) and the channel's GitHub-hosted account (https://github.com/riffomonas).

The name, *Riffomonas*, comes from the concept of "riffing" where musical themes are adapted to achieve a similar sound, albeit perhaps in a different context [@Schloss2018a]. This is to emphasize the value of reproducibility not only to recreate a set of results but to apply a method with a different dataset [@Leek2015]. The channel covers topics related to reproducible data analysis practices including R programming, data visualization, project organization, version control, command line programming, workflow tools, and scientific publishing. Each video includes a brief introduction followed by me live coding to achieve a goal. I emphasize the use of live coding to modulate the rate of instruction and to show viewers my own coding practices. Observing a experienced analyst make mistakes normalizes some level of failure and demonstrates the strategies they can use to resolve their own mistakes. Viewers are encouraged to follow along with each video and to apply the new information to their own project.

Each video emphasizes a specific topic, but includes other content that is selected to review topics covered in recent videos. Although videos can be watched individually, they often form a project arc. For example, between July 2020 and July 2021, I formulated a research question, obtained and analyzed data to answer the question, and wrote a paper that was published in *mSphere* [@Schloss2021]. This series of 67 videos covered every topic from creating the initial directory on my computer to house the project files through reviewing the proofs of the published manuscript. Other project arcs have included visualizing microbiome data, modeling microbiome data using machine learning tools, analyzing the impacts of rarefying microbiome data, and other topics. Going forward, the *Riffomonas* channel will continue to post project-based content to help researchers develop their reproducible research skills.

@@

>>>>

The *Riffomonas* YouTube channel (https://www.youtube.com/c/RiffomonasProject) seeks to fill this gap. I started consistently posting videos at the beginning of the COVID-19 pandemic in April 2020. As of the end of November 2022, the channel included 285 videos that had been viewed 635,947 times; the channel had 11,327 subscribers. The majority of these are 264 videos in the "Code Club" playlist [@Hagan2020] (Table 1). Other videos are related to a previously described tutorial series on reproducible research [@Schloss2018a] and series where reproducible reseach practices are used to address topical questions. Code Club videos are typically between 20 and 30 minutes long. The code that is developed in the videos is available through a website (https://riffomonas.org/code_club/) and the channel's GitHub-hosted account (https://github.com/riffomonas).

The name, *Riffomonas*, comes from the concept of "riffing" where musical themes are adapted to achieve a similar sound, albeit perhaps in a different context [@Schloss2018a]. This is to emphasize the value of reproducibility not only to recreate a set of results but to apply a method with a different dataset [@Leek2015]. The channel covers topics related to reproducible data analysis practices including R programming, data visualization, project organization, version control, command line programming, workflow tools, and scientific publishing (Table 1). Each video includes a brief introduction followed by me live coding to achieve a goal. I emphasize the use of live coding to modulate the rate of instruction and to show viewers my own coding practices. Observing a experienced analyst make mistakes normalizes some level of failure and demonstrates the strategies they can use to resolve their own mistakes. Viewers are encouraged to follow along with each video and to apply the new information to their own project.

Each video emphasizes a specific topic, but includes other content that is selected to review topics covered in recent videos. Although videos can be watched individually, they often form a project arc (Table 1). For example, between July 2020 and July 2021, I formulated a research question, obtained and analyzed data to answer the question, and wrote a paper that was published in *mSphere* [@Schloss2021]. This series of 67 videos covered every topic from creating the initial directory on my computer to house the project files through reviewing the proofs of the published manuscript. Other project arcs have included visualizing microbiome data, modeling microbiome data using machine learning tools, analyzing the impacts of rarefying microbiome data, and other topics. Going forward, the *Riffomonas* channel will continue to post project-based content to help researchers develop their reproducible research skills.

@@

**Table 1. Description of the data science topics and project based series covered in the playlists found on the *Riffomonas* YouTube Channel.** Because most videos cover more than one topic they are found in mutiple playlists. Playlists and counts were current as of December 1, 2022. Playlists can be found under the Playlist tab at https://www.youtube.com/c/RiffomonasProject.

| |  **Number of videos**  |
|:-----------------------------------------|:----------------------:|
| **Videos covering data science topics** |  |
| [Data visualization with R's tidyverse and allied packages](https://youtube.com/playlist?list=PLmNrK_nkqBpKHYucwmN6YlNjoyeWoGBYu) | 146 |
| [Data manipulation within R's tidyverse and other packages](https://youtube.com/playlist?list=PLmNrK_nkqBpKf7j_ewpUm-w33R6PJYtD9) | 116 |
| [Data analysis with base R](https://youtube.com/playlist?list=PLmNrK_nkqBpLaDgAZb5SHHhJ8TDufVv7H) | 39 |
| [Tools for reproducible data analysis](https://youtube.com/playlist?list=PLmNrK_nkqBpLdTEOj_-bwp58490i8ezRI) | 33 |
| [Working at the command line](https://youtube.com/playlist?list=PLmNrK_nkqBpKhP0Jb2XGPoRRfToHF1w-y) | 26 |
| [Literate programming with R markdown](https://youtube.com/playlist?list=PLmNrK_nkqBpKT5Wz1IHZneRXPUGNtB-IG) | 18 |
| [Machine learning with mikropml R package](https://youtube.com/playlist?list=PLmNrK_nkqBpKpzb9-vI4V7SdXC-jXEcmg) | 16 |
| [Version control with git and GitHub](https://youtube.com/playlist?list=PLmNrK_nkqBpJtNdQBPhPWjIFRYeFOGfJ1) | 15 |
| [Scientific writing](https://youtube.com/playlist?list=PLmNrK_nkqBpI7_TMg72ub3Nflk9F8qPlb) | 15 |
| [Project organization](https://youtube.com/playlist?list=PLmNrK_nkqBpKtCHqSSHXZdK-C4Zg89Rrv) | 3 |
|    |
| **Project based series** |  |
| [All Code Club videos since April 2, 2020](https://youtube.com/playlist?list=PLmNrK_nkqBpKY3SZiivlIGvcLX-KHmfR8) | 265 |
| [Microbiome data analysis and visualization](https://youtube.com/playlist?list=PLmNrK_nkqBpIIRdQTS2aOs5OD7vVMKWAi) | 86 |
| [ASV/OTU senstitivity and specificity analyses](https://youtube.com/playlist?list=PLmNrK_nkqBpL7m_tyWdQgdyurerttCsPY) | 67 |
| [Visualizing COVID-19 vaccination attitudes](https://youtube.com/playlist?list=PLmNrK_nkqBpL9STHqSod2LGwciLk9TXZ1) | 31 |
| [Climate change data visualization](https://youtube.com/playlist?list=PLmNrK_nkqBpJTSHf3IsN_K_pjFu58z9Oq) | 29 |
| [Evaluating rarefaction and its alternatives](https://youtube.com/playlist?list=PLmNrK_nkqBpJuhS93PYC-Xr5oqur7IIWf) | 18 |
| [Drought index visualization](https://youtube.com/playlist?list=PLmNrK_nkqBpK6iqwN3QeQyXqI6DrcGgIm) | 17 |
| [Reproducible reserach tutorial series](https://youtube.com/playlist?list=PLmNrK_nkqBpL0d2E26TqPkmTAfelYKbQX) | 14 |
| [Commemorating Juneteenth 2022 with a visualization](https://youtube.com/playlist?list=PLmNrK_nkqBpK24Xzukw7ngIDEeukkunzO) | 5 |
| [2018 MLB All Star Break data analysis sprint](https://youtube.com/playlist?list=PLmNrK_nkqBpLd_IvW37Fm1w5LRv9ggvYI) | 4 |

### 2022-12-20 submission/manuscript.tex
Render with table, edits, and track changes

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{setspace}
\doublespacing
\usepackage[left]{lineno}
\usepackage[none]{hyphenat}
\raggedright
\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
\usepackage[T1]{fontenc}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

The \emph{Riffomonas} YouTube channel
(\url{https://www.youtube.com/c/RiffomonasProject}) seeks to fill this
gap. I started consistently posting videos at the beginning of the
COVID-19 pandemic in the Spring of 2020. As of the end of November 2022,
the channel included 285 videos that had been viewed 635,947 times; the
channel had 11,327 subscribers. The majority of these are 264 videos in
the ``Code Club'' playlist (5). Other videos are related to a previously
described tutorial series on reproducible research (6) and series where
reproducible reseach practices are used to address topical questions.
Code Club videos are typically between 20 and 30 minutes long. The code
that is developed in the videos is available through a website
(\url{https://riffomonas.org/code_club/}) and the channel's
GitHub-hosted account (\url{https://github.com/riffomonas}).

The name, \emph{Riffomonas}, comes from the concept of ``riffing'' where
musical themes are adapted to achieve a similar sound, albeit perhaps in
a different context (6). This is to emphasize the value of
reproducibility not only to recreate a set of results but to apply a
method with a different dataset (7). The channel covers topics related
to reproducible data analysis practices including R programming, data
visualization, project organization, version control, command line
programming, workflow tools, and scientific publishing. Each video
includes a brief introduction followed by me live coding to achieve a
goal. I emphasize the use of live coding to modulate the rate of
instruction and to show viewers my own coding practices. Observing a
experienced analyst make mistakes normalizes some level of failure and
demonstrates the strategies they can use to resolve their own mistakes.
Viewers are encouraged to follow along with each video and to apply the
new information to their own project.

Each video emphasizes a specific topic, but includes other content that
is selected to review topics covered in recent videos. Although videos
can be watched individually, they often form a project arc. For example,
between July 2020 and July 2021, I formulated a research question,
obtained and analyzed data to answer the question, and wrote a paper
that was published in \emph{mSphere} (8). This series of 67 videos
covered every topic from creating the initial directory on my computer
to house the project files through reviewing the proofs of the published
manuscript. Other project arcs have included visualizing microbiome
data, modeling microbiome data using machine learning tools, analyzing
the impacts of rarefying microbiome data, and other topics. Going
forward, the \emph{Riffomonas} channel will continue to post
project-based content to help researchers develop their reproducible
research skills.

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1.0in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{setspace}
\doublespacing
\usepackage[left]{lineno}
\usepackage[none]{hyphenat}
\raggedright
\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
\usepackage[T1]{fontenc}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

The \emph{Riffomonas} YouTube channel
(\url{https://www.youtube.com/c/RiffomonasProject}) seeks to fill this
gap. I started consistently posting videos at the beginning of the
COVID-19 pandemic in April 2020. As of the end of November 2022, the
channel included 285 videos that had been viewed 635,947 times; the
channel had 11,327 subscribers. The majority of these are 264 videos in
the ``Code Club'' playlist (5) (Table 1). Other videos are related to a
previously described tutorial series on reproducible research (6) and
series where reproducible reseach practices are used to address topical
questions. Code Club videos are typically between 20 and 30 minutes
long. The code that is developed in the videos is available through a
website (\url{https://riffomonas.org/code_club/}) and the channel's
GitHub-hosted account (\url{https://github.com/riffomonas}).

The name, \emph{Riffomonas}, comes from the concept of ``riffing'' where
musical themes are adapted to achieve a similar sound, albeit perhaps in
a different context (6). This is to emphasize the value of
reproducibility not only to recreate a set of results but to apply a
method with a different dataset (7). The channel covers topics related
to reproducible data analysis practices including R programming, data
visualization, project organization, version control, command line
programming, workflow tools, and scientific publishing (Table 1). Each
video includes a brief introduction followed by me live coding to
achieve a goal. I emphasize the use of live coding to modulate the rate
of instruction and to show viewers my own coding practices. Observing a
experienced analyst make mistakes normalizes some level of failure and
demonstrates the strategies they can use to resolve their own mistakes.
Viewers are encouraged to follow along with each video and to apply the
new information to their own project.

Each video emphasizes a specific topic, but includes other content that
is selected to review topics covered in recent videos. Although videos
can be watched individually, they often form a project arc (Table 1).
For example, between July 2020 and July 2021, I formulated a research
question, obtained and analyzed data to answer the question, and wrote a
paper that was published in \emph{mSphere} (8). This series of 67 videos
covered every topic from creating the initial directory on my computer
to house the project files through reviewing the proofs of the published
manuscript. Other project arcs have included visualizing microbiome
data, modeling microbiome data using machine learning tools, analyzing
the impacts of rarefying microbiome data, and other topics. Going
forward, the \emph{Riffomonas} channel will continue to post
project-based content to help researchers develop their reproducible
research skills.

@@

\textbf{Table 1. Description of the data science topics and project
based series covered in the playlists found on the \emph{Riffomonas}
YouTube Channel.} Because most videos cover more than one topic they are
found in mutiple playlists. Playlists and counts were current as of
December 1, 2022. Playlists can be found under the Playlist tab at
\url{https://www.youtube.com/c/RiffomonasProject}.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.6364}}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.3636}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\textbf{Number of videos}
\end{minipage} \\
\midrule()
\endhead
\textbf{Videos covering data science topics} & \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpKHYucwmN6YlNjoyeWoGBYu}{Data
visualization with R's tidyverse and allied packages} & 146 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpKf7j_ewpUm-w33R6PJYtD9}{Data
manipulation within R's tidyverse and other packages} & 116 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpLaDgAZb5SHHhJ8TDufVv7H}{Data
analysis with base R} & 39 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpLdTEOj_-bwp58490i8ezRI}{Tools
for reproducible data analysis} & 33 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpKhP0Jb2XGPoRRfToHF1w-y}{Working
at the command line} & 26 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpKT5Wz1IHZneRXPUGNtB-IG}{Literate
programming with R markdown} & 18 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpKpzb9-vI4V7SdXC-jXEcmg}{Machine
learning with mikropml R package} & 16 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpJtNdQBPhPWjIFRYeFOGfJ1}{Version
control with git and GitHub} & 15 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpI7_TMg72ub3Nflk9F8qPlb}{Scientific
writing} & 15 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpKtCHqSSHXZdK-C4Zg89Rrv}{Project
organization} & 3 \\
& \\
\textbf{Project based series} & \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpKY3SZiivlIGvcLX-KHmfR8}{All
Code Club videos since April 2, 2020} & 265 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpIIRdQTS2aOs5OD7vVMKWAi}{Microbiome
data analysis and visualization} & 86 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpL7m_tyWdQgdyurerttCsPY}{ASV/OTU
senstitivity and specificity analyses} & 67 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpL9STHqSod2LGwciLk9TXZ1}{Visualizing
COVID-19 vaccination attitudes} & 31 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpJTSHf3IsN_K_pjFu58z9Oq}{Climate
change data visualization} & 29 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpJuhS93PYC-Xr5oqur7IIWf}{Evaluating
rarefaction and its alternatives} & 18 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpK6iqwN3QeQyXqI6DrcGgIm}{Drought
index visualization} & 17 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpL0d2E26TqPkmTAfelYKbQX}{Reproducible
reserach tutorial series} & 14 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpK24Xzukw7ngIDEeukkunzO}{Commemorating
Juneteenth 2022 with a visualization} & 5 \\
\href{https://youtube.com/playlist?list=PLmNrK_nkqBpLd_IvW37Fm1w5LRv9ggvYI}{2018
MLB All Star Break data analysis sprint} & 4 \\
\bottomrule()
\end{longtable}
